### 2013-02-10 doc/icml2013/model.tex

We would like to recover $B = [\beta_1 | \beta_2 | \cdots | \beta_K]$
and the mixture probabilities $\pi = [\pi_1 | \pi_2 | \cdots | \pi_K]$.

\subsection{Non-linearities}

Approach to handle non-linearities.

Note about dependencies in the n-th moments.

\subsection{Identifiability}

The model is in general identifiable, except for a pathological case
with how data points are placed.

Plot of the above scenario.

Interesting question; how do these extend in the non-linear case (which
would be ``new'').

>>>>

We would like to recover $B = [\beta_1 \mid \beta_2 \mid \cdots \mid \beta_K]$
and the mixture probabilities $\pi = (\pi_1, \pi_2, \dots, \pi_K)$.

Learning framework:
Get $(x^{(1)},y^{(1)})$, ...
don't observe $h$
